Temporal Development of Overlapping Communities in Co-Authorship Networks

### 2015-12-05 paper/paper.tex
references

Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different measurement, detection and evolution of communities and many more.~\cite{barabasi2002evolution, newman2001structure, newman2004coauthorship}

@@

Not only overlapping communities exists in networks, but also communities are structured in an hirarchical way. Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015, Cui201485, Shen20091706}.

@@

\begin{enumerate}
	\item[(1)] Genrate slices of the network for each year.
	\item[(2)] Find function for calculating edge weights.
	\item[(3)] Apply edge weights to each snapshot.
	\item[(4)] Find out $k$.
	\item[(5)] Adjust treshold $w^*$ according to $k$.	
	\item[(6)] Do CPM for each snapshot.
	\item[(7)] Conduct community mapping.
\end{enumerate}

>>>>

Usually those networks are used to study patterns of scientific collaboration in different fields, their development over time, identify key people regarding different measurement, detection and evolution of communities and many more.~\cite{barabasi2002evolution}, \cite{newman2001structure} and \cite{newman2004coauthorship}.

@@

Not only overlapping communities exists in networks, but also communities are structured in an hirarchical way.
Recent work on algorithms detecting hirachical and overlapping sturctures  include~\cite{1367-2630-11-3-033015}, \cite{Cui201485}, \cite{Shen20091706}.

@@

\begin{enumerate}
\small
	\item[(1)] Genrate slices of the network for each year.
	\item[(2)] Find function for calculating edge weights.
	\item[(3)] Apply edge weights to each snapshot.
	\item[(4)] Find out $k$.
	\item[(5)] Adjust treshold $w^*$ according to $k$.	
	\item[(6)] Do CPM for each snapshot.
	\item[(7)] Conduct community mapping.
\end{enumerate}
